\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-09-20 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
deleted CUBIT_GEOCUBIT/run_boundary_definition.py, since the same thing is done better by run_cubit2specfem3d.py

\subsection{Exporting the Mesh with \texttt{cubit2specfem3d.py} }

@@

Once the geometric model volumes in CUBIT are meshed, you prepare
the model for exportation with the definition of material blocks and
boundary surfaces. Thus, prior to exporting the mesh, you need to
define blocks specifying the materials and absorbing boundaries in
CUBIT. This process could be done automatically using the script \texttt{boundary\_definition.py}
if the mesh meets some conditions or manually, following the block
convention:
\begin{description}
\item [{material\_name}] Each material should have a specific block defined
by a unique name. The name convention of the material is to start
with either 'elastic' or 'acoustic'. It must be then followed by a
unique identifier, e.g. 'elastic 1', 'elastic 2', etc. The additional
attributes to the block define the material description.

@@

In directory "CUBIT\_GEOCUBIT" we provide two scripts that can help doing the above tasks of exporting a CUBIT mesh
to SPECFEM3D format automatically for you: "run\_cubit2specfem3d.py" and "run\_boundary\_definition.py".
Just edit them to indicate the path to your local installation of CUBIT and also the name of the *.cub existing CUBIT mesh file
that you want to export to SPECFEM3D format. These scripts will do the conversion for you automatically except assigning material properties
to the different mesh layers. To do so, you will then need to edit the file 
called "nummaterial\_velocity\_file" that will have just been created and change it from the prototype created:

>>>>

\subsection{Exporting the Mesh with \texttt{run\_cubit2specfem3d.py} }

@@

Once the geometric model volumes in CUBIT are meshed, you prepare
the model for exportation with the definition of material blocks and
boundary surfaces. Thus, prior to exporting the mesh, you need to
define blocks specifying the materials and absorbing boundaries in
CUBIT. This process could be done automatically using the script \texttt{run\_cubit2specfem3d.py}
if the mesh meets some conditions or manually, following the block
convention:
\begin{description}
\item [{material\_name}] Each material should have a specific block defined
by a unique name. The name convention of the material is to start
with either 'elastic' or 'acoustic'. It must be then followed by a
unique identifier, e.g. 'elastic 1', 'elastic 2', etc. The additional
attributes to the block define the material description.

@@

In directory "CUBIT\_GEOCUBIT" we provide a script that can help doing the above tasks of exporting a CUBIT mesh
to SPECFEM3D format automatically for you: "run\_cubit2specfem3d.py".
Just edit them to indicate the path to your local installation of CUBIT and also the name of the *.cub existing CUBIT mesh file
that you want to export to SPECFEM3D format. These scripts will do the conversion for you automatically except assigning material properties
to the different mesh layers. To do so, you will then need to edit the file 
called "nummaterial\_velocity\_file" that will have just been created and change it from the prototype created:
